---
title: "Working with Markdown"
author: "Franny Oppenheimer"
date: "2024-01-23"
output: 
  html_document: 
    theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For markdown, use asterisks to *indicate italic text*

Double line return for a new chunk of text like this

Name  
Department of Biology  
University of Vermont  

# Hash marks for headers

## More hashes for progressively

### smaller

#### and smaller

##### headers!!


**bold face this way**

>Offset quote which embeds and looks really nice when you have extended material that you would like to see

Back to plain text

* first line item  
* second item  
   - spacing for indents
   
^superscript^ or ~subscript~

[set up a link with text](website address)

also footnotes^[at bottom of page]


# Also Tables!

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

```
fencing sets boundaries and everything inside the fencing *is shown as literal text* without rendering
```

$$a + b =c$$

we can also use Latex in line with a single dollar sign $a +b=c$ like this

## Subscripts in LaTex

$$ H_0 = Z_{a + b}$$

## Rendering in Plain Text

$$P(occurrence Of Species A) = Z$$

use curly brackets whenever we have amounts of text to get rid of italics

$$P(\mbox{Occurrence of Species A}) = Z$$
 
  
easy to embed LaTex in line like $4 + 4 = 8$

we can also use markdown fencing in line with a single backtick like `4 + 4 = 8`

it's just a stylistic choice

We can even execute r code inside of markdown text: `r 4 + 4` (<-that said 4 + 4)

use r as the first character inside to accomplish this

## Imbedding R Code

backtick backtick backtick squiggly bracket r squiggly bracket

your R code!

backtick backtick backtick


```{r}

#r ```{r eval=TRUE, echo=TRUE}
# eval is whether we're showing the output
# echo is whether we're showing the code

# Use comments extensively in your coding!
Pred <- seq(1,10)       # make a vector of integers from 1 to 10
Res <- runif(10)        # generate 10 draws from a random uniform (0,1) distribution

# Print the random numbers
print(Res)
```

```{r}

# first chunk of code in rmd file
print(pi)
pi + 3


```




